\chapter{Creating an high-level API for automating the multi-modal acquisition}

In the analitycal chemistry routine in general every software allows the user to create a macro to automatize repetitive tasks. This is  in general also a good starting point for a replicable  workflow. The problem is usually that the macro describe only a part of the experiment. The whole experiment can be hardly fully or automatized. This  

The experiment is actually a set of macros, the multi-modal acquisition usually invovles more techniques and experiment. 


https://www.emeraldcloudlab.com/how-it-works

For automating and reporting the procedure of the acquisition a script or a macro is usually used. Every software 


We have hence wrapped the functions of the SDK creating a higher-level abstraction of the actions normally performed during the multi-modal acquisition (e.g. scan the area indicated, acquire spectra of the area). 

Even here we used Python for ideally this process should performed wrapping low-level command set, in our case we mostly used SDK accessible using C\# .dll.

http://pythonnet.github.io/
Protocol 
 standard operating procedure (SOP) is a set of step-by-step instructions compiled 

\section{Level of Detail in the description of the multi-modal analysis}
The concept of level of detail can be implemented also for the multi-modal analysis. Every analyses manaual or automatized can be described by a series of step.

Detail for reproducing the exact procedure
Which is a detail that determine the output
Detail that determine the quality of the output
De

General step for automatized measurement.

\textbf{connection} in this step the communication between the instrument and the terminal is enstablished usuaully the input parameter are usually port and baudrate.



